### 2021-06-22 src/paper/report.tex
More comments.

The four contact networks are chosen so that the most common NPIs can be modeled in
great detail. NPIs affect the number of contacts or the risk of transmitting the disease
upon having physical contact. The effect of different NPIs will generally vary across
contact types. For example, a mandate to work from home will reduce the number of work
contacts to zero for a fraction of the working population. Schools and daycare can be
closed entirely, operate at reduced capacity---including an alternating schedule---, or
implement mitigation measures like masking requirements or air filters
\citep{Lessler2021}. Curfews may reduce the number of contacts in non-work/non-school
settings. In any setting, measures like masking requirements would reduce the
probability of infection associated with a contact \citep{Cheng2021}.

@@

In the model, susceptibility to contracting the SARS-CoV-2 virus is dependent on age. A
possible infection progresses as shown in Figure~\ref{fig:model_disease_progression}. We
differentiate between an initial period of infection without being infectious or showing
symptoms, being infectious (presymptomatic or asymptomatic), showing symptoms, requiring
intensive care, and recovery or death \citep[similar
to][]{Grimm2021}.\comment[id=HM]{Need to look for non-economists}
The probabilities of transitioning between these states depend on age; their duration is
random within intervals calibrated to medical literature (for a detailed description see
Section~\ref{sec:medical_params}). Conditional on the type of contact, infectiousness is
independent of age \citep{Jones2021}.

@@

We include two types of tests. Polymerase chain reaction (PCR) tests reveal whether an
individual is infected or not; there is no uncertainty to the result. PCR tests require
some days to be processed and there are aggregate capacity constraints throughout. In
contrast, rapid antigen tests yield immediate results; after a phase-in period, all tests
that are demanded will be performed. Specificity and sensitivity of these tests is set
according to data analyzed in \cite{Bruemmer2021, Smith2021}; sensitivity depends on the
timing of the test relative to the onset of infectiousness.
Figure~\ref{fig:model_rapid_tests} shows our model for rapid test demand. Schools may
require students to be tested regularly. Rapid tests may be offered by employers for
on-site workers. Individuals may demand tests for private reasons, which include having
plans to meet other people,\footnote{A positive test will make them reduce their
contacts; this is why tests impact the actual contacts in
Figure~\ref{fig:model_description}.} showing symptoms of CoViD-19, and because a
household member tested positively for the virus. We endow each agent with an individual
compliance parameter. This parameter determines whether she takes up rapid tests offered
by employers or follows up on private reasons.\comment[id=HM]{Removed ``and whether she
reduces her contacts if she tests positive or develops symptoms'' -- does not fit here.
If anything, add footnote, but it seems like this is a detail that is just distracting
right here. Make sure to describe clearly and at length in Appendix.}

>>>>

The four contact networks are chosen so that the most common NPIs can be modeled in great
detail. NPIs affect the number of contacts or the risk of transmitting the disease upon
having physical contact. The effect of different NPIs will generally vary across contact
types. For example, a mandate to work from home will reduce the number of work contacts
to zero for a fraction of the working population. Schools and daycare can be closed
entirely, operate at reduced capacity---including an alternating schedule---, or
implement mitigation measures like masking requirements or air filters
\citep{Lessler2021}. Curfews may reduce the number of contacts in
non-work/non-school/non-work settings. In any setting, measures like masking requirements
would reduce the probability of infection associated with a contact \citep{Cheng2021}.

@@

In the model, susceptibility to contracting the SARS-CoV-2 virus is dependent on age. A
possible infection progresses as shown in Figure~\ref{fig:model_disease_progression}. We
differentiate between an initial period of infection without being infectious or showing
symptoms, being infectious (presymptomatic or asymptomatic), showing symptoms, requiring
intensive care, and recovery or death \citep[similar
to][]{Grimm2021}.\comment[id=HM]{Need to look for non-economists} The probabilities of
transitioning between these states depend on age; their duration is random within
intervals calibrated to medical literature (for a detailed description see
Section~\ref{sec:medical_params}). Conditional on the type of contact, infectiousness is
independent of age \citep{Jones2021}.\comment[id=K]{This might be misleading because the
susceptibility to catch the virus \textbf{is} age-dependent.}

@@

We include two types of tests. Polymerase chain reaction (PCR) tests reveal whether an
individual is infected or not; there is no uncertainty to the result. PCR tests require
some days to be processed and there are aggregate capacity constraints throughout. In
contrast, rapid antigen tests yield immediate results; after a phase-in period, all tests
that are demanded will be performed.\comment[id=K]{Might be problematic to talk about
supply and demand here. We don't have supply and demand (except for maybe employers and
employees) and I would not interpret the increases in April as an easing of supply side
constraints.} Specificity and sensitivity of these tests is set according to data
analyzed in \cite{Bruemmer2021, Smith2021}; sensitivity depends on the timing of the test
relative to the onset of infectiousness. Figure~\ref{fig:model_rapid_tests} shows our
model for rapid test demand. Schools may require staff and students to be tested
regularly. Rapid tests may be offered by employers to on-site workers. Individuals may
demand tests for private reasons, which include having plans to meet other people,
showing symptoms of CoViD-19, and because a household member tested positively for the
virus. We endow each agent with an individual compliance parameter. This parameter
determines whether she takes up rapid tests\deleted[id=K]{offered by employers or
follows up on private reasons} % compliance also determines who is tested in education settings
.\footnote{A positive test result (of either kind), as well as symptoms leads most
individuals to reduce their contacts; this is why tests impact the actual contacts in
Figure~\ref{fig:model_description}.}

%%% ===================================================================================
